How to Avoid OOTA Without Really Trying

### 2024-09-13 paper/ootavacuous.tex
ootavacuous: Apply third round September 13 Alan Stern feedback
Suggested-by: Alan Stern <stern@rowland.harvard.edu>
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

All OOTA workers owe a debt of gratitude to the foundational work led
by William Pugh leading to the infamous Java-language
``Causality Test Cases''.\footnote{
	\url{http://www.cs.umd.edu/~pugh/java/memoryModel/unifiedProposal/testcases.html}.}
% %%% Eventually cite P3064.

@@

This section uncovers some semantic-dependency complexities.
Section~\ref{sec:Semantic Dependencies and Source Code}
shows that semantic dependencies are functions of executions,
rather than being strict functions of the source code.
Section~\ref{sec:Semantic Dependencies Can Be Many-To-One}
shows that semantic dependencies do not necessarily extend
from a single load to a single store, but can instead involve
multiple loads.
Section~\ref{sec:Semantic Dependencies Affected by Cross-Thread Optimizations}
shows that semantic dependencies can be affected by cross-thread
optimizations.
Sections~\ref{sec:Semantic Dependencies Affected by if Statements}
and~\ref{sec:Semantic Dependencies Not Affected by if Statements}
show that \co{if} statements can have surprising effects on semantic
dependencies, up to and including eliminating them completely.
Finally,
Section~\ref{sec:Semantic Dependencies and Matching Up Stores}
demonstrates some challenges in determining which of a group of
stores is involved in a given semantic dependency.

>>>>

All OOTA workers owe a debt of gratitude to the foundational work led
by William Pugh, represented by the infamous Java-language
``Causality Test Cases''.\footnote{
	\url{http://www.cs.umd.edu/~pugh/java/memoryModel/unifiedProposal/testcases.html}.}
% %%% Eventually cite P3064.

@@

This section discusses semantic-dependency complexities.
